
\singlespace
\addcontentsline{toc}{part}{НОМ ЗҮЙ}
\begin{thebibliography}{}
	% Ашигласан материалыг эндээс оруулна
	\bibitem{Islam2006}
	R. Islam and S. M. Rasad, ``Employee performance evaluation by the AHP: A case study,'' \emph{Asia Pacific Management Review}, vol. 11, no. 3, pp. 163--176, Jun. 2006. [Online]. Available: \url{https://rafikulislam.com/uploads/myworks/27066075955b8a1b374434.pdf}

	% Reference for Performance Evaluation Methods and Techniques
	\bibitem{Shaout2014}
	A. Shaout and M. K. Yousif, ``Performance evaluation – Methods and techniques survey,'' \emph{MCST Journal}, vol. 3, no. 5, pp. 66--74, Sep. 2014. [Online]. Available: \url{https://d1wqtxts1xzle7.cloudfront.net/41797022/Paper030516-libre.pdf}

	% Reference for Next.js documentation
	\bibitem{NextJS2025}
	Next.js Team, ``Next.js documentation,'' Vercel Inc., 2025. [Online]. Available: \url{https://nextjs.org/docs}

	% Reference for Golang documentation
	\bibitem{Go2025}
	The Go Authors, ``The Go programming language documentation,'' 2025. [Online]. Available: \url{https://go.dev/doc/}

	% Reference for PostgreSQL documentation
	\bibitem{PostgreSQL2025}
	PostgreSQL Global Development Group, ``PostgreSQL documentation,'' 2025. [Online]. Available: \url{https://www.postgresql.org/docs/}

	% Reference for Docker documentation
	\bibitem{Docker2025}
	Docker Inc., ``Docker documentation,'' 2025. [Online]. Available: \url{https://docs.docker.com/}

	% Reference for Performance Management book
	\bibitem{Armstrong2015}
	M. Armstrong, \emph{Performance Management: Key Strategies and Practical Guidelines}, 5th ed. London, UK: Kogan Page, 2015.

	% Reference for Computer Networks book
	\bibitem{Tanenbaum2021}
	A. S. Tanenbaum and D. J. Wetherall, \emph{Computer Networks}, 6th ed. Upper Saddle River, NJ: Pearson, 2021.

\end{thebibliography}